---
title: 'APHRC HH Survey Data'
author: "Steve and Jonathan"
date: " `r as.Date(Sys.time())` "
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 5
    toc_float: yes
---




```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE
	, warning = FALSE
	, message = FALSE
	, fig.width = 10
	, fig.height = 10
	, results = "asis")
options(width = 12)
library("rmarkdown")
```


```{r}
load(".hhamenitiesSummary.RData")

# Keep only objects to be used in the report
#rm(list = ls()[!ls() %in% c(
#         # missProp.Rout
#          "miss_prop_df_html"
#         , "no_vars_droped"
#         , "file_prefix"
#         # idVars.Rout
#         , "id_dup_dis"
#         # backgroundSummary
#         , "hha_sleeprooms_total_issues_counts_html"
#         , "hha_sleeprooms_total_count_plot"
#         , "hha_sleeprooms_total_mean_plot"
#         , "hha_rentablerooms_total_issues_counts_html"
#         , "hha_rentablerooms_total_count_plot"
#         , "hha_rentablerooms_total_mean_plot"
#         , "hha_numpeople_total_issues_counts_html"
#         , "hha_numpeople_total_count_plot"
#         , "hha_numpeople_total_mean_plot"
#         # hhamenitiesSummary
#         , "hha_drinkwatersource_issues_count"
#         , "hha_drinkwatersource_issues_plot"
#         , "hha_drinkwatersource_clean_prop_plot"
#         , "hha_toilet_2to4yrs_issues_count"
#         , "hha_toilet_2to4yrs_issues_plot"
#         , "hha_toilet_2to4yrs_clean_prop_plot"
#      )
#   ]
#)

```


# Data Exploration

## Missingness

```{r}
miss_prop_df_html
```

* A total of `r no_vars_droped` which $100\%$ missingness were dropped

## Duplicated IDs

```{r}
id_dup_dis
```

## Background

### Total number of rooms used by household for sleeping.

#### Probably missing

```{r}
hha_sleeprooms_total_issues_counts_html
```

```{r}
# Plot of the above
hha_sleeprooms_total_count_plot 
```

#### Average

```{r}
hha_sleeprooms_total_mean_plot 
```


### Total number of rentable rooms available.

#### Probably missing cases

```{r}
hha_rentablerooms_total_issues_counts_html
```

```{r}
# Plot of the above
hha_rentablerooms_total_count_plot 
```

#### Average

```{r}
hha_rentablerooms_total_mean_plot 
```

### Total number of people living in this household.

#### Probably missing cases

```{r}
hha_numpeople_total_issues_counts_html
```

```{r}
# Plot of the above
hha_numpeople_total_count_plot
```

#### Average

```{r}
hha_numpeople_total_mean_plot
```

## Household amenities

### Total number of people living in this household.

#### Probably missing cases

```{r}
hha_drinkwatersource_issues_count
```

```{r}
# Plot of the above
hha_drinkwatersource_issues_plot
```

#### Proportions

```{r}
hha_drinkwatersource_clean_prop_plot
```


### Kind of toilet facility (2-4 years)

#### Probably missing cases

```{r}
hha_toilet_2to4yrs_issues_count
```

```{r}
hha_toilet_2to4yrs_issues_plot
```

#### Proportions

```{r}
hha_toilet_2to4yrs_clean_prop_plot
``` 

```{r}
rm(list = ls())
```




